---
output: rmarkdown::github_document
---

`infermedica` : R API Interface to the Infermedica API

The following functions are implemented:

- `im_add_evidence`:	Add evidence to a diagnosis request object
- `im_add_patient_info`:	Add patient info to a diagnosis request object
- `im_get_condition`:	Retrieve info for a specific symptom
- `im_get_diagnosis`:	Send built diagnosis request to Infermedica API
- `im_get_risk_factors`:	Retrieve info for a specific lab test
- `im_get_symptom`:	Retrieve info for a specific symptom
- `im_info`:	Retrieve Infermedica API info
- `im_list_conditions`:	Retrieve list of conditions from Infermedica API
- `im_list_lab_tests`:	Retrieve list of lab tests from Infermedica API
- `im_list_risk_factors`:	Retrieve list of risk factors from Infermedica API
- `im_list_symptoms`:	Retrieve list of symptoms from Infermedica API
- `im_lookup`:	Returns a single observation matching given phrase from Infermedica API
- `im_searc`:	Returns list of observations matching the given phrase from Infermedica API
- `im_start_diagnosis`:	Start building a diagnosis request object for the Infermedica API

### Installation

```{r eval=FALSE}
devtools::install_git("https://gitlab.com/hrbrmstr/infermedica.git")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
library(infermedica)

# current verison
packageVersion("infermedica")

```

### Test Results

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
library(infermedica)
library(testthat)

date()

test_dir("tests/")
```

