---
output: rmarkdown::github_document
---

`infermedica` : R Interface to the Infermedica API

A set of tools that provide programmatic access to the Infermedica medical
inference engine API. Functions are provided that enable uploading of patient’s health
data (such as symptoms, risk factors, lab tests results or demographics) to the
Infermedica AI inference engine which will analyze it and return a list of likely
conditions and relevant observations to verify. For more information please visit
<http://infermedica.com>.

The following functions are implemented:

- `im_add_evidence`:	Add evidence to a diagnosis request object
- `im_add_patient_info`:	Add patient info to a diagnosis request object
- `im_get_condition`:	Retrieve info for a specific symptom
- `im_get_diagnosis`:	Send built diagnosis request to Infermedica API
- `im_get_risk_factors`:	Retrieve info for a specific lab test
- `im_get_symptom`:	Retrieve info for a specific symptom
- `im_info`:	Retrieve Infermedica API info
- `im_list_conditions`:	Retrieve list of conditions from Infermedica API
- `im_list_lab_tests`:	Retrieve list of lab tests from Infermedica API
- `im_list_risk_factors`:	Retrieve list of risk factors from Infermedica API
- `im_list_symptoms`:	Retrieve list of symptoms from Infermedica API
- `im_lookup`:	Returns a single observation matching given phrase from Infermedica API
- `im_search`:	Returns list of observations matching the given phrase from Infermedica API
- `im_start_diagnosis`:	Start building a diagnosis request object for the Infermedica API

### TODO

- implement `explain`
- implement missing components in `diagnosis`

### Installation

```{r eval=FALSE}
devtools::install_git("https://gitlab.com/hrbrmstr/infermedica.git")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
library(infermedica)

# current verison
packageVersion("infermedica")

```

### Test Results

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
library(infermedica)
library(testthat)

date()

test_dir("tests/")
```

